Implementing DNS in C0

### 2017-11-17 proposal.tex
minor wording changes

However, the protocol is also able to characterize processes that are
not completely sequential, and branch into different sequences as they
encounter choices. This typing system, also, guarantees that data is
send and received in the correct order and by the correct processes
(session fidelity), and that the communication is always one-to-one.
The \Kwd{CC0} programming language is secure in terms of both memory
and communication safety.

>>>>

However, the protocol is also able to characterize processes that are
not completely sequential, and branch into different sequences as they
encounter choices. This typing discipline also guarantees that data is
sent and received in the correct order and by the correct processes
(an invariant called \emph{session fidelity}), and that the
communication is always one-to-one.
